---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xlsxread

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/xlsxread)](https://CRAN.R-project.org/package=xlsxread)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![R build status](https://github.com/Clement-LVD/xlsxread/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Clement-LVD/xlsxread/actions)
[![Codecov test coverage](https://codecov.io/gh/Clement-LVD/xlsxread/graph/badge.svg)](https://app.codecov.io/gh/Clement-LVD/xlsxread)
<!-- badges: end -->

`xlsxread::` is an R package. The goal of `xlsxread::` is to import an Excel .xlsx sheet within the R environnement with `xlsxread::readxlsx()`. 

> Dependencies are kept as low as possible and quick reading is expected.

> - ðŸŒ Read .xlsx file from an URL or a file path 
> - ðŸš€ Maximal performance for quick reading 
> - â„› `base::` R with no dependencies 

## Installation

You can install the development version of `xlsxread::` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Clement-LVD/xlsxread")
```

## Examples

Import a sheet from .xlsx file with ` xlsxread::readxlsx()`

- online :

```{r example}

datas <- xlsxread::readxlsx(url = "https://go.microsoft.com/fwlink/?LinkID=521962"
                            , sheet = 1, remove_first_row_as_header = TRUE)

str(datas)

student <- xlsxread::readxlsx(url = "https://www.exceldemy.com/wp-content/uploads/2023/12/Project-Management-Sample-Data.xlsx"
                              , skip_rows = 1:4, remove_first_row_as_header = TRUE)

str(student)

```

- from a local file :

```{r example2}

datas <- xlsxread::readxlsx(filepath =  "C:/me/fake_datas.xlsx", sheet = 1)


```

